---
title: "Code for Coding Assesment"
output: html_document
author: "Samir Fidai"
---


Loading the Tidyverse package

```{r, output = FALSE}
library(tidyverse)

```



Uploading the csv into R and converting the dates using lubridate. 

```{r}
research <- read.csv(here::here("F-F_Research_Data_Factors_daily.CSV"), skip = 4)
research <- research %>% mutate(X = as.numeric(X),
                                X = lubridate::ymd(X)) %>%
  filter(!is.na(Mkt.RF))


research %>% head()
```

Calculating the Summary Statistics

```{r, output = TRUE}
summary_statistics <- research %>%
  select(-X) %>%
  psych::describe() 
summary_statistics
```

Creating the Density plots for the Market and Risk-Free assets 

```{r}
Mkt.RF_Density <- research %>% ggplot(aes(x=Mkt.RF)) +
  geom_histogram(aes(y=..density..), bins = 100) +
  geom_density(aes(Mkt.RF), color = "Red")

RF_Density <- research %>% ggplot(aes(x=RF)) +
  geom_histogram(aes(y=..density..), bins = 30) +
  geom_density(aes(RF), color = "Red")

gridExtra::grid.arrange(Mkt.RF_Density, RF_Density)
```

Code for generating the growth of One Dollar invested from the beginning. 

```{r}
research %>% mutate(summed = 1 + cumsum(Mkt.RF)) %>%
  ggplot(aes(X, summed)) +
  geom_line() +
  ylab("Closing") +
  xlab("Year") +
  ggtitle("Growth of a Dollar")

```

Grouped by year and generated plot.

```{r}
research.ByYear <- research %>%
  group_by(year = lubridate::floor_date(X, unit = "years")) %>%
  summarise(`Sum Mkt.RF` = sum(Mkt.RF))


research.ByYear %>% ggplot(aes(year, (1 + cumsum(`Sum Mkt.RF`)))) +
  geom_line()
```


Created and populated the matrix of Bootstraped values.

```{r}
set.seed(1738)
n = 25
B = 10000

bootstrap_Matrix <- matrix(
  sample(research.ByYear$`Sum Mkt.RF`, size = B*n, replace = TRUE),
  ncol = B, nrow = n)

One_Matrix <- matrix(1, ncol = B, nrow = 1)

bootstrap_Matrix <- rbind(One_Matrix, bootstrap_Matrix)

dim(bootstrap_Matrix)



```

Matrix is converted to a dataframe using the melt() function. Using the new Dataframe, the initial graph of the 10,000 Bootstraps was generated.

```{r}
melted_Bootstrap <- bootstrap_Matrix %>% reshape2::melt() %>%
  group_by(Var2) %>%
  mutate(`value Sum` = cumsum(value)) 

Bootstrap_chart <- melted_Bootstrap %>%
  ggplot() +
  geom_line(aes(x = Var1 , y = `value Sum`, group = Var2)) + 
  theme_minimal() 

Bootstrap_chart
```

The 5th and 95th percentiles are located using quantile()

```{r}
melted_Bootstrap_pivot_wider <- melted_Bootstrap %>% 
  select(-value) %>%
  pivot_wider(names_from = Var1, values_from = `value Sum`) %>%
  as_tibble()

psych::describe(melted_Bootstrap_pivot_wider$`26`)

quantile(melted_Bootstrap_pivot_wider$`26`, 0.95)
quantile(melted_Bootstrap_pivot_wider$`26`, 0.05)
quantile(melted_Bootstrap_pivot_wider$`26`, 0.5)

melted_Bootstrap_pivot_wider %>% filter(`26` == 42.96 | `26` == 355.36)


```

The 5th and 95th percentiles are highlited in the initial graph.

```{r}
Bootstrap_plot_percentiles <- melted_Bootstrap %>% 
  filter(Var2 == 6173 | Var2 == 9811) 
  

Bootstrap_chart <- Bootstrap_chart + geom_line(data = Bootstrap_plot_percentiles, aes(x = Var1 , y = `value Sum`, group = Var2, color = "Dark Red")) +
  theme_gray() +
  ylab("Close") +
  xlab("Year") +
  ggtitle("Bootstrap simulations of Growth of $1") +
  theme(legend.position = "NONE") 

Bootstrap_chart
```


CAGR calculations

```{r}
CAGR <- melted_Bootstrap %>%
  filter(Var1 == 26) %>%
  mutate(CAGR = (`value Sum`/1)^(1/25)-1)

CAGR %>% ggplot() +
  geom_histogram(aes(CAGR), bins = 150)


```


Comparing the original strategy of 100% investment in the market and a 50-50 split in the market and in risk-free assets using a generated ggplot of #2

```{r}
research %>% 
  mutate(`summed Mkt.RF` = .50 + cumsum(Mkt.RF),
         `summed RF` = .50 + cumsum(RF),
          total = `summed Mkt.RF` + `summed RF`) %>%
  ggplot(aes(X, total)) +
  geom_line(aes(X, total), color = "firebrick1") +
  geom_line(aes(X, y = (1 + cumsum(Mkt.RF))), color = "darkolivegreen4") +
  ylab("Closing") +
  xlab("Year") +
  ggtitle("Growth of a Dollar")
```

